---
title: "Bayesian Network Environmental Risk Assessment of Pharmaceuticals"
output: html_notebook
---

Code for messing around with maps of Norway and WWTP by county.

# 1. Setup

```{r packages}
# Setup Renv for reproducible packages
# renv::init()
# renv::restore()
options(renv.download.override = utils::download.file)

# Library
library(tidyverse)
library(splmaps)
library(readxl)
library(glue)

# Leaflet stuff
library(splmaps)
options("rgdal_show_exportToProj4_warnings"="none")
library(sf)
library(leaflet)
library(rgdal)
library(shiny)

`%notin%` <- negate(`%in%`)

# Disable summarise informative message:
options(dplyr.summarise.inform = FALSE)
```

# 2. Data
Import Statistics Norway and Norwegian Institute for Public Health (NIPH) data and maps.
```{r data_import}
# Various Statistics Norway datasets
source(file = "src/data_importers/statistics_norway_import.R")
# SPL maps from the Norwegian Institute for Public Health
source(file = "src/data_importers/spl_map_import.R")

# Sales weights for 8 high-risk APIs, adapted from NIPH data
source(file = "src/data_importers/API_sales_import.R")
# Filter to the 6 APIs used in the Bayesian Network
analysed_APIs <- c("estradiol", "ethinylestradiol", "diclofenac", 
                      "ibuprofen", "paracetamol", "ciprofloxacin")
API_sales_weights_1999_2018 <- API_sales_weights_1999_2018 %>% 
  filter(API_Name %in% analysed_APIs)
# API PNECs from various sources
source(file = "src/data_importers/API_PNEC_import.R")

# Norwegian and English classifications of WWT technologies
source(file = "src/data_importers/WWT_class_import.R")

# van Dijk et al.'s unpublished pharmaceutical removal rates dataset
source(file = "src/data_importers/WWT_removal_import.R")
# match names using InChIKeys and filter results
API_removal_rates <- API_removal_rates %>% 
  left_join(API_sales_weights_1999_2018 %>% select(API_Name, InChIKey_string), 
            by = "InChIKey_string") %>% 
  distinct() %>% 
  mutate(API_Name = case_when(InChIKey_string == "mean" ~ "mean",
        TRUE ~ API_Name)) %>% 
  filter(!is.na(API_Name))
```


# 3. Methods

```{r data_processing_geographic}
# Summarise share of total population and WWTP class access by county (2020)
source(file = "src/data_processing/pop_share_county.R")
source(file = "src/data_processing/WWTP_share_county.R")
```

Population discretisation was manually performed in Hugin, rounding population (in millions) up to the 
next highest 0.5. This is replicated here so we can check our choices of LM parameters.

```{r data_processing_population}
# Discretise population for diagnostic/summary graphs
source(file = "src/data_processing/pop_discretisation_Norway.R")
```


Calculate a linear model of Sales weight (kg), explained by population (mil) and year, plus
an intercept. This is used to predict sales weights under various population scenarios to 2050.

```{r data_processing_API}
# Fit linear models to sales data
source(file = "src/data_processing/API_sales_LM.R")
```

We can automate running through all possible combinations of APIs and scenarios in Hugin using
a data file (essentially a CSV) with scenario variables filled in, and specially formatted empty
columns for variables we want to pull out.

```{r data_processing_Hugin}
source(file = "src/data_exporters/WWT_share_CPT_exporter.R")

source(file = "src/data_processing/R_to_Hugin.R")
```

Now re-import data from Hugin

```{r data_import_Hugin}
source(file = "src/data_importers/Hugin_to_R_importer.R")
```

```{r data_processing_maps}
source(file = "src/data_processing/map_preparation.R")
```

# 4. Results

NB: Try different Viridis-style colour scheme throughout

```{r graphics theme}
viridis_colour <- c("viridis", "magma", "plasma", "inferno")[4]
```

```{r shiny_map}
source(file = "src/interactive_graphics/shiny_data_viewer.R")
shinyApp(ui, server)

avg_RQ_county %>% 
    filter(API_Name == "Total",
           master_pop_scenario == "Main") %>% 
    group_by(master_year, County_Name) %>% 
    summarise(mean(Avg_RQ)) %>% 
    arrange(County_Name) %>% 
    ungroup() %>% 
    group_by(County_Name) %>% 
    summarise(perc_increase = max(`mean(Avg_RQ)`) / min(`mean(Avg_RQ)`))
```

```{r WWTP_bar}
source(file = "src/graphics/WWTP_RQ_bars.R")
WWTP_RQ_bars
```

```{r pop_scen_bar}
source(file = "src/graphics/pop_scen_RQ_bars.R")
pop_scen_RQ_bars
```

```{r combined_risk_bar}
source(file = "src/graphics/combined_risk_bar.R")
```