---
title: "Bayesian Network Environmental Risk Assessment of Pharmaceuticals"
output: html_notebook
---

Code for messing around with maps of Norway and WWTP by county.

# 1. Setup

```{r packages}
# Setup Renv for reproducible packages
# renv::init()
# renv::restore()
options(renv.download.override = utils::download.file)
# Update to a new version of R
# renv::upgrade() 
# renv::hydrate(update = "all") # populates the renv cache with copies of up to 
#                               # date package versions, needed by the project
#   # renv::update() should have no effect now, but running it as well won't harm 
#   # to check that all packages are indeed up to date
# renv::snapshot() # inspect the message before confirming to overwrite renv.lock

# Library
library(tidyverse)
library(splmaps)
library(readxl)
library(glue)

# Leaflet stuff
library(splmaps)
library(rgdal)
options("rgdal_show_exportToProj4_warnings"="none")
library(sf)
library(leaflet)
library(shiny)
library(svglite)
library(scatterpie)
library(scico)
library(cowplot)

`%notin%` <- negate(`%in%`)

# Disable summarise informative message:
options(dplyr.summarise.inform = FALSE)
```

# 2. Data
Import Statistics Norway and Norwegian Institute for Public Health (NIPH) data and maps.
```{r data_import}
# Various Statistics Norway datasets
source(file = "src/data_importers/statistics_norway_import.R")
# SPL maps from the Norwegian Institute for Public Health
source(file = "src/data_importers/spl_map_import.R")

# Sales weights for 8 high-risk APIs, adapted from NIPH data
source(file = "src/data_importers/API_sales_import.R")
# Filter to the 6 APIs used in the Bayesian Network
analysed_APIs <- c("estradiol", "ethinylestradiol", "diclofenac", 
                      "ibuprofen", "paracetamol", "ciprofloxacin")
API_sales_weights_1999_2018 <- API_sales_weights_1999_2018 %>% 
  filter(API_Name %in% analysed_APIs)
# API PNECs from various sources
source(file = "src/data_importers/API_PNEC_import.R")

# # Norwegian and English classifications of WWT technologies
# source(file = "src/data_importers/WWT_class_import.R")

# van Dijk et al.'s unpublished pharmaceutical removal rates dataset
source(file = "src/data_importers/WWT_removal_import.R")
# match names using InChIKeys and filter results
API_removal_rates <- API_removal_rates %>% 
  left_join(API_sales_weights_1999_2018 %>% select(API_Name, InChIKey_string), 
            by = "InChIKey_string") %>% 
  distinct() %>% 
  mutate(API_Name = case_when(InChIKey_string == "mean" ~ "mean",
        TRUE ~ API_Name)) %>% 
  filter(!is.na(API_Name))
```


# 3. Methods

```{r data_processing_geographic}
# Summarise share of total population by county (2020)
source(file = "src/data_processing/pop_share_county.R")
```

Population discretisation was manually performed in Hugin, rounding population (in millions) up to the 
next highest 0.5. This is replicated here so we can check our choices of LM parameters.

```{r data_processing_population}
# Discretise population for diagnostic/summary graphs
source(file = "src/data_processing/pop_discretisation_Norway.R")
```

```{r data_processing_maps}
# Set up a base map of Norway
source(file = "src/data_processing/map_preparation.R")
```

```{r map_of_counties}
source(file = "src/graphics/WWTP_share_map.R")

# Norway_county_WWT_map 
# ggsave(filename = "output/images/raw/figure02_map_WWT.svg", device = "svg", 
#        width = 5, height = 10, units = "cm")
# 
# Norway_county_pies_WWT
# ggsave(filename = "output/images/raw/figure02_pies_WWT.svg", device = "svg", 
#        width = 20, height = 10, units = "cm")
# 
# API_removal_rates_bars
# ggsave(filename = "output/images/raw/figure02_bars_removal.svg", device = "svg", 
#        width = 20, height = 5, units = "cm")

```

Calculate a linear model of Sales weight (kg), explained by population (mil) and year, plus
an intercept. This is used to predict sales weights under various population scenarios to 2050.

```{r data_processing_API}
# YAH 15:14 - 13/01/2023 - changed the year value in the lm to n - 2000, now
# need to tweak the rest accordingly
# Fit linear models to sales data, and predict future sales from models
source(file = "src/data_processing/API_sales_LM.R")
# Graph out predictions from LMs
source(file = "src/graphics/sales_prediction_graph.R")
figure03_lm_graphs +
  theme_minimal()

ggsave(filename = "output/images/raw/figure03_lm_graphs.svg", device = "svg", 
       width = 23, height = 12, units = "cm")
```

We can automate running through all possible combinations of APIs and scenarios in Hugin using
a data file (essentially a CSV) with scenario variables filled in, and specially formatted empty
columns for variables we want to pull out.

```{r data_processing_Hugin}
# This turned out to be hard to do automatically, so I did it by hand.
# source(file = "src/data_exporters/WWT_share_CPT_exporter.R")

source(file = "src/data_processing/R_to_Hugin.R")


```

Now re-import data from Hugin

```{r data_import_Hugin}
source(file = "src/data_importers/Hugin_to_R_importer.R")
```

TODO: Experiment with colours more when it's a more relevant issue. 
https://brushingupscience.com/2019/10/01/default-colormaps-are-parula-and-viridis-really-an-improvement-over-jet/
https://www.vis4.net/palettes/#/20|d|00429d,96ffea,ffffe0|ffffe0,ff005e,93003a|1|1

```{r graphics theme}
viridis_colour <- c("viridis", "magma", "plasma", "inferno")[4]

# Set a consistent mapping of RQs to scale values
viridis_RQ_mapping <- Hugin_Data_Output_Tall %>% 
    select(Risk_Bin) %>% 
    filter(Risk_Bin %notin% c("true", "false")) %>% 
    distinct() %>% 
        pull()

API_labeller <- str_to_title(pull(LMs_API[1]))
names(API_labeller) <- API_labeller
API_labeller <- c(API_labeller, AllAPI = "All APIs")
county_labels <- as_labeller(c(Viken = "Viken (Urban)",
                               Nordland = "Nordland (Rural)",
                               Oslo = "Oslo (Urban)",
                               `Whole Country` = "Whole Country",
                               API_labeller))
```

# 4. Results

```{r simple_map}
source(file = "src/graphics/RQ_map_year.R")

# Save as SVG for modification
Norway_county_pies_RQ

ggsave(filename = "output/images/raw/figure04a_pies_RQ.svg", device = "svg", 
       width = 20, height = 10, units = "cm")

Norway_county_RQ_map

ggsave(filename = "output/images/raw/figure04b_map_RQ.svg", device = "svg", 
       width = 20, height = 10, units = "cm")

Norway_county_bars_RQ <- Norway_county_bars_RQ +
    theme(legend.position = "none")

plot_grid(Norway_county_RQ_map, Norway_county_bars_RQ, 
          align = "v", 
          nrow = 2, rel_heights = c(2, 1))

ggsave(filename = "output/images/raw/figure04bc_map_bars_RQ.svg", device = "svg", 
       width = 25, height = 15, units = "cm")

```

```{r WWTP_bar}
source(file = "src/graphics/WWTP_RQ_bars.R")
WWTP_RQ_bars

ggsave(filename = "output/images/ready/figure05_wwtp_scenario_RQ.png", device = "png", 
       width = 20, height = 10, units = "cm")
```

```{r pop_scen_bar}
source(file = "src/graphics/pop_scen_RQ_bars.R")
pop_scen_RQ_bars

ggsave(filename = "output/images/ready/figure06_pop_scenario_RQ.png", device = "png", 
       width = 20, height = 10, units = "cm")
```

```{r combined_risk_bar}
source(file = "src/graphics/combined_risk_bar.R")
combined_RQ_bars

ggsave(filename = "output/images/ready/figure07_combined_RQ.png", device = "png", 
       width = 23, height = 15, units = "cm")
```